---
title: "Burstiness Regresssions & Analyses"
output:
  html_document:
    df_print: paged
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = FALSE}
setwd("")
print(getwd())
library("httpgd")
library("ggplot2")
library("paletteer")
library("sjPlot")
library("dplyr")
library("tidyr")
library("lme4")
library("scico")
library(ggokabeito)
library(cowplot)

```
### read in data
```{r, echo = FALSE}
#read in CHILDES data
data_childes <- read.csv("CSVS/b_values_childes_24.csv")
data_childes <- na.omit(data_childes)
#print(head(data_childes))

#read in Daylong data
data_daylong <- read.csv("CSVS/daylong_adjusted_mcdi_values.csv")
data_daylong <- na.omit(data_daylong)
#print(head(data_daylong))


# read in daylong sampled data - 15 minutes
data_daylong_sampled_15 <- read.csv("CSVS/daylong_sampled_cdi_15minutes.csv")
data_daylong_sampled_15 <- na.omit(data_daylong_sampled_15)

# read in daylong sampled data - 5 minutes
data_daylong_sampled_5 <- read.csv("CSVS/daylong_sampled_cdi_5minutes.csv")
data_daylong_sampled_5 <- na.omit(data_daylong_sampled_5)

merged_childes_daylong <- merge(data_childes, data_daylong, by = "Word",
                   suffixes = c("_dataCHILDES", "_dataDaylong"))
                
merged_childes_daylongsampled_15 <- merge(data_childes, data_daylong_sampled_15, by = "Word",
                   suffixes = c("_dataCHILDES", "_dataDaylongSampled15"))
merged_daylong_daylongsampled15 <- merge(data_daylong, data_daylong_sampled_15, by = "Word",
                   suffixes = c("_dataDaylong", "data_daylong_sampled_15"))

merged_daylong_daylongsampled5 <- merge(data_daylong, data_daylong_sampled_5, by = "Word",
                   suffixes = c("_dataDaylong", "data_daylong_sampled_5"))
merged_childes_daylongsampled5 <- merge(data_childes, data_daylong_sampled_5, by = "Word",
                   suffixes = c("_dataChildes", "data_daylong_sampled_5"))

merged_daylongsampled15_daylongsampled5 <- merge(data_daylong_sampled_15, data_daylong_sampled_5, by = "Word",
                   suffixes = c("_dataDaylong_sampled15", "data_daylong_sampled_5"))
```

```{r}

```


# CORRELATIONS: WITHIN CORPORA (Table 3)
## (CHILDES) 
### Burstiness & Frequency
- correlations between CHILDES burstiness & frequency
```{r, echo = FALSE}
data <- data_childes
print("All Classes")
print(cor.test(x = data$Log_Mean_Frequency, y = data$Mean_Burstiness))

print("Nouns")
subset <- data[data$Lexical_Class == "Noun", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Verbs")
subset <- data[data$Lexical_Class == "Verb", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Adjectives")
subset <- data[data$Lexical_Class == "Adjective", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Functions")
subset <- data[data$Lexical_Class == "Function", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))
```

## (DAYLONG)
### Burstiness & Frequency
- correlation between Daylong burstiness & frequency 
```{r, echo = FALSE}
data <- data_daylong
print("All Classes")
print(cor.test(x = data$Log_Mean_Frequency, y = data$Mean_Burstiness))

print("Nouns")
subset <- data[data$Lexical_Class == "Noun", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Verbs")
subset <- data[data$Lexical_Class == "Verb", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Adjectives")
subset <- data[data$Lexical_Class == "Adjective", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Functions")
subset <- data[data$Lexical_Class == "Function", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))
```



## DAYLONG SAMPLED
### Burstiness & Frequency
- correlation between Daylong SAMPLED 15 burstiness & frequency 
```{r, echo = FALSE}
data <- data_daylong_sampled_15
print("All Classes")
print(cor.test(x = data$Log_Mean_Frequency, y = data$Mean_Burstiness))

print("Nouns")
subset <- data[data$Lexical_Class == "Noun", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Verbs")
subset <- data[data$Lexical_Class == "Verb", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Adjectives")
subset <- data[data$Lexical_Class == "Adjective", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Functions")
subset <- data[data$Lexical_Class == "Function", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))
```

- correlation between Daylong SAMPLED 5 burstiness & frequency 
```{r, echo = FALSE}
data <- data_daylong_sampled_5
print("All Classes")
print(cor.test(x = data$Log_Mean_Frequency, y = data$Mean_Burstiness))

print("Nouns")
subset <- data[data$Lexical_Class == "Noun", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Verbs")
subset <- data[data$Lexical_Class == "Verb", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Adjectives")
subset <- data[data$Lexical_Class == "Adjective", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))

print("Functions")
subset <- data[data$Lexical_Class == "Function", ]
print(cor.test(x = subset$Log_Mean_Frequency, y = subset$Mean_Burstiness))
```


# CORRELATIONS: CORPUS-CORPUS CORRELATIONS (TABLE 4 & 5)
## CHILDES & DAYLONG (adjusted)
- correlation between CHILDES & Daylong 
```{r}
# merge datasets 
data_merged <- merge(data_childes, data_daylong, by = "Word",
                   suffixes = c("_dataCHILDES", "_dataDaylong"))
head(data_merged)
```
### Burstiness 
- correlation between CHILDES burstiness & Daylong burstiness
```{r, echo = FALSE}
print("Overall")
print(cor.test(x = data_merged$Mean_Burstiness_dataCHILDES, y = data_merged$Mean_Burstiness_dataDaylong))

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Noun", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylong))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Verb", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylong))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Adjective", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylong))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Function", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylong))

```

### Frequency
- correlation between CHILDES frequency & Daylong  frequency
```{r}
print("Overall")
cor.test(x = data_merged$Log_Mean_Frequency_dataCHILDES, y = data_merged$Log_Mean_Frequency_dataDaylong)

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Noun", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylong))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Verb", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylong))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Adjective", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylong))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Function", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylong))
```

## CHILDES & Daylong SAMPLED 
### correlations between CHILDES and Daylong SAMPLED 15
```{r}
# merge datasets 
merged_childes_daylongsampled <- merge(data_childes, data_daylong_sampled_15, by = "Word",
                   suffixes = c("_dataCHILDES", "_dataDaylongSampled"))
head(merged_childes_daylongsampled)
```
- correlations between CHILDES burstiness and Daylong SAMPLED burstiness
```{r}
data_merged <- merged_childes_daylongsampled
print("Overall")
cor.test(x = data_merged$Mean_Burstiness_dataCHILDES, y = data_merged$Mean_Burstiness_dataDaylongSampled)

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Noun", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Verb", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Adjective", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Function", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylongSampled))
```
- correlations between CHILDES frequency and Daylong SAMPLED frequency
```{r}
data_merged <- merged_childes_daylongsampled
print("Overall")
cor.test(x = data_merged$Log_Mean_Frequency_dataCHILDES, y = data_merged$Log_Mean_Frequency_dataDaylongSampled)

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Noun", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Verb", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Adjective", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Function", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylongSampled))
```

###- correlations between CHILDES and Daylong SAMPLED 5 
```{r}
# merge datasets 
merged_childes_daylongsampled <- merge(data_childes, data_daylong_sampled_5, by = "Word",
                   suffixes = c("_dataCHILDES", "_dataDaylongSampled"))
head(merged_childes_daylongsampled)
```
- correlations between CHILDES burstiness and Daylong SAMPLED burstiness
```{r}
data_merged <- merged_childes_daylongsampled
print("Overall")
cor.test(x = data_merged$Mean_Burstiness_dataCHILDES, y = data_merged$Mean_Burstiness_dataDaylongSampled)

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Noun", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Verb", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Adjective", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Function", ]
print(cor.test(x = subset$Mean_Burstiness_dataCHILDES, y = subset$Mean_Burstiness_dataDaylongSampled))
```
- correlations between CHILDES frequency and Daylong SAMPLED frequency
```{r}
data_merged <- merged_childes_daylongsampled
print("Overall")
cor.test(x = data_merged$Log_Mean_Frequency_dataCHILDES, y = data_merged$Log_Mean_Frequency_dataDaylongSampled)

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Noun", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Verb", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Adjective", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataCHILDES == "Function", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataCHILDES, y = subset$Log_Mean_Frequency_dataDaylongSampled))
```
## Daylong & Daylong SAMPLED  
### correlations between Daylong and Daylong SAMPLED 15
```{r}
# merge datasets 
merged_daylong_daylongsampled <- merge(data_daylong, data_daylong_sampled_15, by = "Word",
                   suffixes = c("_dataDaylong", "_dataDaylongSampled"))
head(merged_daylong_daylongsampled)
```
- correlations between Daylong burstiness and Daylong SAMPLED burstiness
```{r}
data_merged <- merged_daylong_daylongsampled
print("Overall")
cor.test(x = data_merged$Mean_Burstiness_dataDaylong, y = data_merged$Mean_Burstiness_dataDaylongSampled)

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Noun", ]
print(cor.test(x = subset$Mean_Burstiness_dataDaylong, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Verb", ]
print(cor.test(x = subset$Mean_Burstiness_dataDaylong, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Adjective", ]
print(cor.test(x = subset$Mean_Burstiness_dataDaylong, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Function", ]
print(cor.test(x = subset$Mean_Burstiness_dataDaylong, y = subset$Mean_Burstiness_dataDaylongSampled))
```
- correlations between Daylong frequency and Daylong SAMPLED frequency
```{r}
data_merged <- merged_daylong_daylongsampled
print("Overall")
cor.test(x = data_merged$Log_Mean_Frequency_dataDaylong, y = data_merged$Log_Mean_Frequency_dataDaylongSampled)

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Noun", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataDaylong, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Verb", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataDaylong, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Adjective", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataDaylong, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Function", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataDaylong, y = subset$Log_Mean_Frequency_dataDaylongSampled))
```
### correlations between Daylong and Daylong SAMPLED 5
```{r}
# merge datasets 
merged_daylong_daylongsampled <- merge(data_daylong, data_daylong_sampled_5, by = "Word",
                   suffixes = c("_dataDaylong", "_dataDaylongSampled"))
head(merged_daylong_daylongsampled)
```
- correlations between Daylong burstiness and Daylong SAMPLED burstiness
```{r}
data_merged <- merged_daylong_daylongsampled
print("Overall")
cor.test(x = data_merged$Mean_Burstiness_dataDaylong, y = data_merged$Mean_Burstiness_dataDaylongSampled)

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Noun", ]
print(cor.test(x = subset$Mean_Burstiness_dataDaylong, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Verb", ]
print(cor.test(x = subset$Mean_Burstiness_dataDaylong, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Adjective", ]
print(cor.test(x = subset$Mean_Burstiness_dataDaylong, y = subset$Mean_Burstiness_dataDaylongSampled))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Function", ]
print(cor.test(x = subset$Mean_Burstiness_dataDaylong, y = subset$Mean_Burstiness_dataDaylongSampled))
```
- correlations between Daylong frequency and Daylong SAMPLED frequency
```{r}
data_merged <- merged_daylong_daylongsampled
print("Overall")
cor.test(x = data_merged$Log_Mean_Frequency_dataDaylong, y = data_merged$Log_Mean_Frequency_dataDaylongSampled)

print("Nouns")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Noun", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataDaylong, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Verbs")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Verb", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataDaylong, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Adjectives")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Adjective", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataDaylong, y = subset$Log_Mean_Frequency_dataDaylongSampled))

print("Functions")
subset <- data_merged[data_merged$Lexical_Class_dataDaylong == "Function", ]
print(cor.test(x = subset$Log_Mean_Frequency_dataDaylong, y = subset$Log_Mean_Frequency_dataDaylongSampled))
```




# MODELS: (TABLES 6,7,8.9)
## CHILDES DATA
```{r}
#print(summary(data_childes))
print(table(data_childes$Lexical_Class))
cat("\nCHILDES:\t\tMean Burstiness:\t", mean(data_childes$Mean_Burstiness),"(", sd(data_childes$Mean_Burstiness), ")\tMean Frequency:\t", mean(data_childes$Log_Mean_Frequency),"(", sd(data_childes$Log_Mean_Frequency), ")\t\tN:", nrow(data_childes))
```
[CHILDES DATA] WordBank ~  Log_Mean_Frequency * Mean_Burstiness     
- overall / all lexical classes 
```{r, echo = FALSE}
print("[CHILDES DATA] MODEL: WordBank ~  Log_Mean_Frequency * Mean_Burstiness")
data <-data_childes

lm_childes_overall <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = data)
print(summary(lm_childes_overall))
```

- Nouns only 
```{r, echo = FALSE}
data <-data_childes
subset <- data[data$Lexical_Class == "Noun", ]
lm_childes_nouns <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_childes_nouns)
```
- Verbs only 
```{r, echo = FALSE}
data <-data_childes
subset <- data[data$Lexical_Class == "Verb", ]
lm_childes_verbs <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_childes_verbs)
```

- Adjectives only 
```{r, echo = FALSE}
data <-data_childes
subset <- data[data$Lexical_Class == "Adjective", ]
lm_childes_adj <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_childes_adj)
```

- Function words only 
```{r, echo = FALSE}
data <-data_childes
subset <- data[data$Lexical_Class == "Function", ]
lm_childes_function <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_childes_function)
```




## MODELS: DAYLONG  DATA 
```{r, echo = FALSE}
data_daylong$Lexical_Class.f <-factor(data_daylong$Lexical_Class)
print(table(data_daylong$Lexical_Class))
cat("\nDAYLONG :\tMean Burstiness:\t", mean(data_daylong$Mean_Burstiness),"(", sd(data_daylong$Mean_Burstiness), ")\tMean Log Frequency:\t", mean(data_daylong$Log_Mean_Frequency),"(", sd(data_daylong$Log_Mean_Frequency), ")\t\tN:", nrow(data_daylong))
```
[DAYLONG DATA] MODEL: WordBank ~  Log_Mean_Frequency * Mean_Burstiness
- overall / all lexical classes 
```{r}
data <-data_daylong
lm_daylongadj_overall <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = data)
print(summary(lm_daylongadj_overall))
```
- Nouns only 
```{r}
data <-data_daylong
subset <- data[data$Lexical_Class == "Noun", ]
lm_daylongadj_nouns <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_nouns)
```
- Verbs only 
```{r}
data <-data_daylong
subset <- data[data$Lexical_Class == "Verb", ]
lm_daylongadj_verb <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_verb)
```
- Adjectives only 
```{r}
data <-data_daylong
subset <- data[data$Lexical_Class == "Adjective", ]
lm_daylongadj_adj <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_adj)
```
- Function words only 
```{r}
data <-data_daylong
subset <- data[data$Lexical_Class == "Function", ]
lm_daylongadj_fun <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_fun)
```



## MODELS: DAYLONG SAMPLED (15 min) DATA 
```{r, echo = FALSE}
data_daylong_sampled <- data_daylong_sampled_15
data_daylong_sampled$Lexical_Class.f <-factor(data_daylong_sampled$Lexical_Class)
#summary(data_daylong_adjusted)
print(table(data_daylong_sampled$Lexical_Class))
cat("\nDAYLONG ADJUSTED:\tMean Burstiness:\t", mean(data_daylong_sampled$Mean_Burstiness),"(", sd(data_daylong_sampled$Mean_Burstiness), ")\tMean Frequency:\t", mean(data_daylong_sampled$Log_Mean_Frequency),"(", sd(data_daylong_sampled$Log_Mean_Frequency), ")\t\tN:", nrow(data_daylong_sampled))
```


[DAYLONG SAMPLED DATA] MODEL: WordBank ~  Log_Mean_Frequency * Mean_Burstiness
- overall / all lexical classes 
```{r}
data <-data_daylong_sampled
lm_daylongadj_overall <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = data)
print(summary(lm_daylongadj_overall))
```
- Nouns only 
```{r}
data <-data_daylong_sampled
subset <- data[data$Lexical_Class == "Noun", ]
lm_daylongadj_nouns <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_nouns)
```
- Verbs only 
```{r}
data <-data_daylong_sampled
subset <- data[data$Lexical_Class == "Verb", ]
lm_daylongadj_verb <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_verb)
```
- Adjectives only 
```{r}
data <-data_daylong_sampled
subset <- data[data$Lexical_Class == "Adjective", ]
lm_daylongadj_adj <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_adj)
```
- Function words only 
```{r}
data <-data_daylong_sampled
subset <- data[data$Lexical_Class == "Function", ]
lm_daylongadj_fun <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_fun)
```

## MODELS: DAYLONG SAMPLED (5 min) DATA 
```{r, echo = FALSE}
data_daylong_sampled_5$Lexical_Class.f <-factor(data_daylong_sampled_5$Lexical_Class)
#summary(data_daylong_adjusted)
print(table(data_daylong_sampled_5$Lexical_Class))
cat("\nDAYLONG ADJUSTED:\tMean Burstiness:\t", mean(data_daylong_sampled_5$Mean_Burstiness),"(", sd(data_daylong_sampled_5$Mean_Burstiness), ")\tMean Frequency:\t", mean(data_daylong_sampled_5$Log_Mean_Frequency),"(", sd(data_daylong_sampled_5$Log_Mean_Frequency), ")\t\tN:", nrow(data_daylong_sampled_5))
```

[DAYLONG SAMPLED DATA] MODEL: WordBank ~  Log_Mean_Frequency * Mean_Burstiness
- overall / all lexical classes 
```{r}
data <-data_daylong_sampled_5
lm_daylongadj_overall <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = data)
print(summary(lm_daylongadj_overall))
```
- Nouns only 
```{r}
data <-data_daylong_sampled_5
subset <- data[data$Lexical_Class == "Noun", ]
lm_daylongadj_nouns <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_nouns)
```
- Verbs only 
```{r}
data <-data_daylong_sampled_5
subset <- data[data$Lexical_Class == "Verb", ]
lm_daylongadj_verb <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_verb)
```
- Adjectives only 
```{r}
data <-data_daylong_sampled_5
subset <- data[data$Lexical_Class == "Adjective", ]
lm_daylongadj_adj <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_adj)
```
- Function words only 
```{r}
data <-data_daylong_sampled_5
subset <- data[data$Lexical_Class == "Function", ]
lm_daylongadj_fun <- lm(WordBank ~  Mean_Burstiness * Log_Mean_Frequency, data = subset)
summary(lm_daylongadj_fun)
```